---
output: 
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# testlib

[![Travis-CI Build Status](https://travis-ci.org/rsquaredacademy/testlib.svg?branch=master)](https://travis-ci.org/rsquaredacademy/testlib)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/testlib?branch=master&svg=true)](https://ci.appveyor.com/project/rsquaredacademy/testlib)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/testlib)](http://cran.r-project.org/package=testlib)
[![Coverage Status](https://img.shields.io/codecov/c/github/rsquaredacademy/testlib/master.svg)](https://codecov.io/github/rsquaredacademy/testlib?branch=master)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active)
[![GitHub issues](https://img.shields.io/github/issues/rsquaredacademy/testlib.svg)](https://github.com/rsquaredacademy/testlib/issues)
[![Twitter](https://img.shields.io/twitter/url/https/github.com/rsquaredacademy/testlib.svg?style=social)](https://twitter.com/intent/tweet?text=Wow:&url=%5Bobject%20Object%5D)

## Overview

testlib is a demo R package created to explore the different aspects of R package development. Hadley Wickham's book [R Packages](http://r-pkgs.had.co.nz/) was used as a guide for developing this package. The package contains a function for creating two way tables of categorical data and visualizing such tables using bar and mosaic plots. Learn more in `vignette("testlib")` or `?cross_table`.


## Installation

testlib is not currently available from CRAN, but you can install the development version from github:

[![GitHub version](https://badge.fury.io/gh/rsquaredacademy%2Ftestlib.svg)](https://badge.fury.io/gh/rsquaredacademy%2Ftestlib)

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("rsquaredacademy/testlib")
```


## Usage

The main function in the pacakge is `cross_table()` which creates two way tables of categorical data.

```{r ctable}
library(testlib)
k <- testlib::cross_table(mtcars$cyl, mtcars$am)
k
```

## License

[![License](http://img.shields.io/:license-mit-blue.svg)](https://github.com/rsquaredacademy/testlib/blob/master/LICENSE)
