---
title: "Two Way Tables"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Two Way Tables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Two way tables are useful in exploring the relationship between categorical 
variables. This vignette summarizes the following functions available in the `testlib` package to create and visualize two way tables:


- `cross_table`
- `barplot.cross_table`
- `mosaicplot.cross_table`

```{r, echo=FALSE, message=FALSE}
library(testlib)
```

Create a two way table by specifying the two categorical variables, the 
relationship between which is being explored.

```{r}
k <- cross_table(mtcars$cyl, mtcars$am)
k
```

Visualize the two way tables in the following plots:

- Bar Plot

```{r fig.width=5, fig.height=5,fig.align='center'}
k <- cross_table(mtcars$cyl, mtcars$am)
plot(k)
```

- Grouped Bar Plot

```{r fig.width=5, fig.height=5,fig.align='center'}
k <- cross_table(mtcars$cyl, mtcars$am)
plot(k, beside = TRUE)
```

- Proportional Bar Plot

```{r fig.width=5, fig.height=5,fig.align='center'}
k <- cross_table(mtcars$cyl, mtcars$am)
plot(k, beside = FALSE, proportional = TRUE)
```

- Mosaic Plot

```{r fig.width=5, fig.height=5,fig.align='center'}
k <- cross_table(mtcars$cyl, mtcars$am)
mosaicplot(k)
```
